Simulation Summary Figures

### 2018-08-09 datasets/simulations/simulations-summary.Rmd
Fix links/names broken after moving analysis/changing res names

---
title: "Simulation Summary Figures (simulations)"
author: "Rafalab"
output: 
    html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

## load helper functions
for (f in list.files("../datasets/R", "\\.(r|R)$", full.names = TRUE)) {
    source(f)
}

@@

```{r, fig.width = 10, fig.height = 4}
res_pi0 <- dplyr::filter(resmet, setting == "varyingpi0-lowsignal", alpha == 0.05)

@@

```{r, fig.width = 10, fig.height = 4}
res_info <- dplyr::filter(resmet, setting == "varyinginfo-lowsignal", alpha == 0.05)

>>>>

---
title: "Simulation Summary Figures"
author: "Patrick Kimes"
output: 
    html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

## load helper functions
for (f in list.files("../R", "\\.(r|R)$", full.names = TRUE)) {
    source(f)
}

@@

```{r, fig.width = 10, fig.height = 4}
res_pi0 <- dplyr::filter(resmet, setting == "varyingpi0", alpha == 0.05)

@@

```{r, fig.width = 10, fig.height = 4}
res_info <- dplyr::filter(resmet, setting == "varyinginfo", alpha == 0.05)
